### 2013-06-29 inst/doc/vingette.Rmd
updated documentation
documentation updated
Updated readme generated from inst/doc/vignette.Rmd

R package for reading, writing, integrating and publishing data using the Ecological Metadata Language (EML) format.

@@

<!-- r highlighting on github is broken, so we'll use {r} codeblocks -->

```{r}
#install_github("reml", "ropensci")
library("reml")
```

@@

```{r}
 eml$set(givenName = "Carl", surName = "Boettiger", email = "cboettig@ropensci.org")
```

@@

See the [EML generated](https://github.com/ropensci/eml/tree/master/inst/examples/my_eml_data.xml) by this example.

@@

@@

@@

>>>>

An R package for reading, writing, integrating and publishing data using the Ecological Metadata Language (EML) format.

* Maintainer: Carl Boettiger
* Authors: Carl Boettiger, Matt Jones, Karthik Ram, Duncan Temple Lang
* License: [CC0](http://creativecommons.org/publicdomain/zero/1.0/)
* This is a dynamic document, generated by [knitr](http://yihui.name/knitr) using [vignette.Rmd](https://github.com/ropensci/reml/blob/master/inst/doc/vingette.Rmd) as the source.

```{r include=FALSE}
source("~/.knitr_defaults.R")
```

@@

```{r}
library("devtools")
install_github("XMLSchema", "omegahat")
install_github("reml", "ropensci")
library("reml")
```

@@

```{r}
 eml$set(contact_givenName = "Carl", contact_surName = "Boettiger", contact_email = "cboettig@ropensci.org")
```

@@

See the [EML generated](https://github.com/ropensci/eml/tree/master/inst/doc/my_eml_data.xml) by this example.

#### In development.

* See [Open issues in writing EML](https://github.com/ropensci/reml/issues?labels=write+eml&page=1&state=open)

@@

Once we have generated a basic EML file, we can publish it to a variety
of academic repositories where it will be indexed, permenently archived,
more easily citable, and publicly discoverable.

In this example, we will publish the above
EML to [figshare](http://figshare.com) using the
[rfigshare](https://github.com/ropensci/rfigshare) package. Like most
academic repostories, figshare requires some basic metadata for any entry.
Much of this we can automatically extract from our existing EML file. 
Additional metadata unique to figshare (e.g. matching it's allowed "categories"
can also be provided.

```{r publish_figshare, eval=FALSE} <!-- We don't want to generate a DOI every time we run the vignette -->
id = eml_publish("my_eml_data.xml", description="Example EML file from reml", categories = "Ecology", tags = "EML")
```

In return, figshare provides the object with a DOI, which is added to the EML.

```{r figshare_doi, eval=FALSE}
doc <- eml_read("my_eml_data.xml")
citation(doc)
```

For the sake of completeness, the explicitly figshare metadata is also written into a 
dedicated `<additionalMetadata>` node with the attribute `id = figshare`.  This allows
us to distinguish between metadata that is an is not available to figshare's indexing,
e.g. if we use the figshare search tool.

#### In development

See [Open issues in publishing EML](https://github.com/ropensci/reml/issues?labels=publish+eml&page=1&state=open)

@@

#### In development

See [Open issues in reading EML](https://github.com/ropensci/reml/issues?labels=read+eml&page=1&state=open)

@@

#### In development

See [Open issues in integrating EML](https://github.com/ropensci/reml/issues?labels=integrate+eml&page=1&state=open)
